On hyperparameter tuning through Lipschitz global optimization

### 2023-09-06 2023/ITMO paper/elsarticle-template-num.tex
minor corrections

\author[UNN,ITMO]{Konstantin Barkalov}
\author[UNN,ITMO]{Denis Karchkov}
\author[UNN,ITMO]{Evgeny Kozinov}
\author[UNN,ITMO]{Ilya Lebedev}
\author[UNN,ITMO]{Denis Rodionov}
\author[UNN,ITMO]{Marina Usova}

@@

The iOpt framework of intelligent optimization methods was developed as part of the ``Strong Artificial Intelligence in Industry'' project. It is designed to select optimal (in a given metric) values of parameters of complex objects and processes, for example, artificial intelligence and machine learning methods. The framework allows fine-tuning of parameters of models and methods used in applied research in various fields of science.  The iOpt framework was designed in the Python programming language using its standard library. To use the framework, you need to have the Python interpreter version 3.8 or higher installed. The framework is open source and is available at \url{https://github.com/aimclub/iOpt}.

@@

\section*{Code availability}
The software that implements all of the described methods is available in the open repository \url{https://github.com/aimclub/iOpt/}.

>>>>

\author[UNN,ITMO]{Konstantin Barkalov\corref{cor}}
\cortext[cor]{Corresponding author: \url{konstantin.barkalov@itmm.unn.ru}}
\author[UNN,ITMO]{Denis Karchkov}
\author[UNN,ITMO]{Evgeny Kozinov}
\author[UNN,ITMO]{Ilya Lebedev}
\author[UNN,ITMO]{Denis Rodionov}
\author[UNN,ITMO]{Marina Usova}

@@

The iOpt framework of intelligent optimization methods is designed to select optimal (in a given metric) values of parameters of complex objects and processes, especially artificial intelligence and machine learning methods. The framework allows fine-tuning of parameters of models and methods used in applied research in various fields of science.  The iOpt framework was designed in the Python programming language using its standard library. To use the framework, you need to have the Python interpreter version 3.8 or higher installed. The framework is open source and is available at \url{https://github.com/aimclub/iOpt}.

@@

\section*{Code availability}
The software that implements all of the described methods is available in the open repository \url{https://github.com/aimclub/iOpt/}.
Python scripts that reproduce the results of the presented experiments are available at \url{https://github.com/aimclub/iOpt/benchmarks}.
